### 2020-02-18 ChapterBackground/chapterBackground.tex
Updated: More in Online Gaming in Background

\subsection{Collision Detection}
Objects are represented by geometry colliders. Collision detection works by detecting overlaps between geometry representations.
Typically objects have simple colliders, such as boxes, capsules, cylinders and spheres. More complex colliders are often supported, such as convex and concave hulls. Colliders can either be static or dynamic.

@@

\subsection{Client-Server}
Client-Server architecture is an architecture in which the game is executed and game state is managed entirely by the server. Clients connect to the server and receive the necessary information about the game world. All messages and interactions are sent through the game server and the server is responsible for disseminating messages to the appropriate clients. The main challenge with this approach is scalability, as a single server can only support a limited number of players. This is normally solved with the addition of more servers, i.e. switching to a distributed server architecture. As all communication goes through the server, clients do not directly communicate with each other, meaning latency can be increased for interactions with other players.
As there is only one central version of the game state, consistency resolution is simplified to solving inconsistencies between server and client and the server treated as the correct master copy. In addition, fault-tolerance is simplified to keeping a single backup of the central server's sate, although this adds more complexity and cost, and can reduce scalability. Client-Server architectures are less prone to cheating than peer-to-peer based architectures, as the game provider has complete control over the game state \cite{P2PSurvey}.

@@

\subsection{Peer-to-Peer}
Peer-to-Peer, often referred to as`P2P', is an architecture in which the game is executed and game state is managed entirely by the peers, although peers are often only responsible for a subset of the game state, such as the entities they are currently interacting with. A peer-to-peer architecture is shown in Fig. \ref{fig_P2P}. Peers are all responsible for message forwarding to each other. In other words, peers act as bother server and client. Peer-to-Peer reduces the cost for the game provider of maintaining expensive servers and can reduce latency between players, as communication is performed directly between peers, rather than communicating through a server. In addition, it provides scalability in terms of compute power, as the more peers that join, the more resources available to the system. However, as more peers join, the greater the communication overhead is between peers. In addition, peer-to-peer is prone to the problems of fault-tolerance, data consistency and cheating by players. A peer is more likely to fail or experience unscheduled disconnection than a dedicated server. As each peer is responsible for the game state, it is possible for communication errors to occur, resulting in two peers with different game states or a peer maliciously altering the game state or the messages being sent to other peers in order to cheat. The fault-tolerance requirements of peer-to-peer can be reduced in short-session-based games, making these architectures better suited to those games \cite{P2PSurvey}. Peer-to-Peer architectures have received much research attention in previous years, with many solutions that attempt to address the problems above, through the use of techniques discussed in \cite{P2PSurvey}.

@@

\subsection{Hybrid Peer-to-Peer}
\subsection{Distributed server}

% problem of maintaining data consistency between peers but does not provide any measures of protection against cheating.

%Unsuitable for real-time physics as latency is too high

>>>>

\subsection{Collision Detection}\label{collision_detection}
Objects are represented by geometry colliders. Collision detection works by detecting overlaps between geometry representations.
Typically objects have simple colliders, such as boxes, capsules, cylinders and spheres. More complex colliders are often supported, such as convex and concave hulls. Colliders can either be static or dynamic.

@@

\subsection{Client-Server}
Client-Server architecture is a type of architecture in which the game is executed and game state is managed entirely by the server. Clients connect to the server and receive the necessary information about the game world. All messages and interactions are sent through the game server and the server is responsible for disseminating messages to the appropriate clients. The main challenge with this approach is scalability, as a single server can only support a limited number of players. This is normally solved with the addition of more servers, i.e. switching to a distributed server architecture. As all communication goes through the server, clients do not directly communicate with each other, meaning latency can be increased for interactions with other players.
As there is only one central version of the game state, consistency resolution is simplified to solving inconsistencies between server and client and the server treated as the correct master copy. In addition, fault-tolerance is simplified to keeping a single backup of the central server's sate, although this adds more complexity and cost, and can reduce scalability. Client-Server architectures are less prone to cheating than peer-to-peer based architectures, as the game provider has complete control over the game state \cite{P2PSurvey}.

@@

\subsection{Peer-to-Peer}
Peer-to-Peer, often referred to as`P2P', is a type of architecture in which the game is executed and game state is managed entirely by the peers, although peers are often only responsible for a subset of the game state, such as the entities they are currently interacting with. A peer-to-peer architecture is shown in Fig. \ref{fig_P2P}. Peers are all responsible for message forwarding to each other. In other words, peers act as bother server and client. Peer-to-Peer reduces the cost for the game provider of maintaining expensive servers and can reduce latency between players, as communication is performed directly between peers, rather than communicating through a server. In addition, it provides scalability in terms of compute power, as the more peers that join, the more resources available to the system. However, as more peers join, the greater the communication overhead is between peers. In addition, peer-to-peer is prone to the problems of fault-tolerance, data consistency and cheating by players. A peer is more likely to fail or experience unscheduled disconnection than a dedicated server. As each peer is responsible for the game state, it is possible for communication errors to occur, resulting in two peers with different game states or a peer maliciously altering the game state or the messages being sent to other peers in order to cheat. The fault-tolerance requirements of peer-to-peer can be reduced in short-session-based games, making these architectures better suited to those games \cite{P2PSurvey}. Peer-to-Peer architectures have received much research attention in previous years, with many solutions that attempt to address the problems above, through the use of techniques discussed in \cite{P2PSurvey}.

@@

\subsection{Hybrid Peer-to-Peer}
Hybrid Peer-to-Peer architectures are a combination of client-server and peer-to-peer architectures. The peer-to-peer part of the system can be responsible for different aspects of the system, including Cooperative Message Dissemination, State Distribution, Basic Server Control and distributing software updates. \cite{P2PSurvey}. Hybrid Peer-to-Peer enable trade-offs between consistency control and scalability are enabled, depending on how the system is divided between server and peer-to-peer.
%These can be broadly classified into two types: Homogeneous, in which all nodes have similar responsibilities and Heterogeneous, in which some peers be

\subsection{Distributed server}
Distributed server or Multi-Server architectures use multiple servers and the computational workload is divided between the servers. This approach enables scalability as more servers are used, so more players can be supported. Fault-tolerance is potentially higher than a single server solution, even if no backup system is employed, as only players connected to the failing server will be affected.

% Game can be divided up in very different ways. Shards, regions (migratory), player-based (non-migratory)
% One server can overloaded if the workload is too high in one region
% Dynamic load-balancing schemes can be employed
% Hand-off between regions is complicated for players, let alone real-time physics
